### 2014-03-10 doc/main.tex
Struktura projektu

\documentclass[a4paper]{article}
\usepackage{polski}
\input{packages}
\title{Cośtam}
\author{Mateusz Grotek 186816 \and Paweł Tarasiuk 186875}
\date{}
\begin{document}
\maketitle
\tableofcontents
\end{document}